### 2025-06-06 short/sections/summary.tex
Update summary.tex

\textcolor{black}{I am a post-doctoral researcher in Computational Social Science at the Institute of Public Administration, Faculty of Governance and Global Affairs, Leiden University, the Netherlands. I hold a DPhil (PhD) in Politics from the University of Oxford, UK, and prior to that, I completed an MA (1st) in Political Science and a BA (2:1) in Government at the Universidad de Chile.}

\textcolor{black}{From an earlier focus on cabinets and civil service, I have developed an active research agenda on how emerging technologies ---including AI--- shape policymaking and the organisation of bureaucracies. My work has appeared in {\itshape Social Science Computer Review}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The International Journal of Press/Politics}, {\itshape The British Journal of Politics and International Relations} and elsewhere.}

\textcolor{black}{During my current postdoctoral appointment, I am mainly contributing to an NWO-funded project on automated text analysis of investment data, investigating how governance structures shape sustainable investments. Specifically, I use Natural Language Processing (NLP) and text-as-data methods to identify patterns and topics within large-scale textual corpora. In addition, I teach the Institutions of Governance and Development course at Leiden University College.}
\vspace{1mm}
\end{cvparagraph}

>>>>

\textcolor{black}{I am a post-doctoral researcher in Computational Social Science at Leiden University’s Institute of Public Administration, Faculty of Governance and Global Affairs, in the Netherlands. I hold a DPhil (PhD) in Politics from the University of Oxford and previously earned an MA in Political Science and a BA in Public Administration and Government from the Universidad de Chile.}

\textcolor{black}{My work bridges the fields of comparative politics, public administration, and computational social science. I build large-scale text-as-data pipelines, deploy AI and machine learning models, and apply causal inference strategies to gain insights into executive politics and elite behaviour. This agenda centres on cabinet reshuffles, ministerial survival, civil service dynamics, and blame-shifting, while also engaging with broader debates on policy agendas, bureaucratic careers, and digital governance.}

\textcolor{black}{My recent peer-reviewed articles have appeared in {\itshape Social Science Computer Review}, {\itshape Public Opinion Quarterly}, {\itshape World Development}, {\itshape Artificial Intelligence and Law}, {\itshape Government and Opposition}, among others. I regularly present at IPSA, ECPR, EPSA and COMPTEXT. I am currently working on an NWO-funded project that uses Large Language Models (LLMs) to analyse global investment prospectuses and reveal how governance arrangements shape sustainable finance flows. In parallel, I contribute to COST Action CA22150 on executive-bureaucratic careers and lead the Enlace-Inserción UDP 2025-2026 project “Unpacking the Unpredictable: Using NLP and LLMs to Examine Cabinet Politics and Responses to Stochastic Events in Presidential Democracies.”}

\textcolor{black}{In addition to research, I convene the undergraduate course Institutions of Governance and Development at Leiden University College and deliver doctoral lectures on data mining and AI at Universidad Diego Portales.}
\vspace{1mm}
\end{cvparagraph}
